%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Ryo Suzuki} % Your name
% \address{\today} % Your secondary addess (optional)
% \address{123 Broadway \\ City, State 12345} % Your address
\address{ryo.suzuki@colorado.edu \\ +1 (650) 485-3567 \\ http://ryosuzuki.org } % Your phone number and email
\address{DLC 170, University of Colorado Boulder, Boulder CO 80302}

\begin{document}

\begin{rSection}{Education}

{\bf Ph.D student in Computer Science, University of Colorado Boulder} \hfill {\em August 2015 - Present} 

{\bf M.A in Economics, University of Tokyo} \hfill {\em March 2013} \\
GPA: 3.9, Top 5\% (A+) in Machine Learning, Microeconomics, and Macroeconomics

{\bf B.Eng in Engineering, Tokyo Institute of Technology} \hfill {\em March 2011} \\ 
GPA: 3.9

\end{rSection}

%----------------------------------------------------------------------------------------


\begin{rSection}{Research Experience}

{\bf University of Colorado Boulder HCI Group} \hfill {\em August 2015 - Present} \\
Advisor: Tom Yeh and Mark D. Gross

{\bf Keio University ERATO Project} \hfill {\em December 2017 - Present} \\
Advisor: Yasuaki Kakehi and Yoshihiro Kawahara

{\bf UC Berkeley BiD Group} \hfill {\em May 2016 - August 2016} \\
Advisor: Bjoern Hartmann

{\bf Stanford University HCI Group} \hfill {\em May 2015 - August 2015} \\
Advisor: Michael S. Bernstein

{\bf University of Tokyo IIS-Lab} \hfill {\em September 2014 - May 2015} \\
Advisor: Koji Yatani

{\bf AIST Media Interaction Group} \hfill {\em January 2015 - March 2015} \\
Advisor: Jun Kato

\end{rSection}


\begin{rSection}{Publications}

{\bf Ryo Suzuki}, Koji Yatani, Mark D. Gross, Tom Yeh,
{\it ``Tabby: Explorable Design for 3D Printing Textures.''},
Proceedings of the ACM Conference on Designing Interactive Systems. ACM, 2018
(DIS'18, in submission)

{\bf Ryo Suzuki}, Jun Kato, Mark D. Gross, Tom Yeh,
{\it ``Reactile: Programming Swarm User Interfaces through Direct Physical Manipulation.''},
Proceedings of the CHI Conference on Human Factors in Computing Systems. ACM, 2018. 
(CHI'18, acceptance rate: 25\%)

Hyunjoo Oh, Tung D. Ta, {\bf Ryo Suzuki}, Mark D. Gross, Yoshihiro Kawahara, Lining Yao,
{\it ``PEP (3D Printed Electronic Papercrafts): An Integrated Approach for 3D Sculpting Paper-based Electronic Devices.''},
Proceedings of the CHI Conference on Human Factors in Computing Systems. ACM, 2018. 
(CHI'18, acceptance rate: 25\%)

{\bf Ryo Suzuki}, Abigale Stangl, Mark D Gross, Tom Yeh,
{\it ``FluxMarker: Enhancing Tactile Graphics with Dynamic Tactile Markers.''}, 
Proceedings of the International ACM SIGACCESS Conference on Computers and Accessibility. ACM, 2017. 
(ASSETS'17, acceptance rate: 26\%)

{\bf Ryo Suzuki}, Gustavo Soares, Andrew Head, Elena Glassman, Ruan Reis, Melina Mongiovi, Loris D'Antoni, Bjoern Hartmann,
{\it ``TraceDiff: Debugging Unexpected Code Behavior Using Trace Divergences.''},
Proceedings of the IEEE Symposium on Visual Languages and Human-Centric Computing. IEEE, 2017. 
(VL/HCC'17, acceptance rate: 29\%)

Andrew Head, Elena Glassman, Gustavo Soares, {\bf Ryo Suzuki}, Lucas Figueredo, Loris D'Antoni, Bjoern Hartmann, 
{\it ``Writing Reusable Code Feedback at Scale with Mixed-Initiative Program Synthesis.''}, 
Proceedings of the ACM Conference on Learning at Scale. ACM, 2017. 
(L@S'17, acceptance rate: 22\%)

Reudismam Rolim, Gustavo Soares, Loris D'Antoni, Oleksandr Polozov, Sumit Gulwani, Rohit Gheyi, {\bf Ryo Suzuki}, Bjoern Hartmann, 
{\it ``Learning Syntactic Program Transformations from Examples.''}, 
Proceedings of the International Conference on Software Engineering. IEEE, 2017. 
(ICSE'17, acceptance rate: 19\%)

{\bf Ryo Suzuki}, Niloufar Salehi, Michelle S. Lam,
Juan C. Marroquin, Michael S. Bernstein,
{\it ``Atelier: Repurposing Expert Crowdsourcing Tasks as Micro-internships.''}, 
Proceedings of the CHI Conference on Human Factors in Computing Systems. ACM, 2016. 
(CHI'16, acceptance rate: 23\%)

\end{rSection}


% {\bf Ryo Suzuki}, Jun Kato, Koji Yatani, {\it "ClassCode: A Web-based Environment for Programming Education in Classrooms."} (VL/HCC'17 in submission)

% {\bf Ryo Suzuki}, Tom Yeh, Koji Yatani, Mark D. Gross, {\it "Autocomplete Textures for 3D Printing."} (CHI'17 under review)

\begin{rSection}{Posters, Demos, and Workshop Papers}

{\bf Ryo Suzuki}, Gustavo Soares, Elena Glassman, Andrew Head, Loris D’Antoni, Bjoern Hartmann,
{\it ``Exploring the Design Space of Automatically Synthesized Hints for Introductory Programming Assignments.''},
Proceedings of the CHI Conference on Human Factors in Computing Systems. ACM, 2017. (CHI'17 Late-Breaking Work)

Stanford Crowd Research Collective (For the full author list, please see the publication), 
{\it ``Daemo: A Self-Governed Crowdsourcing Marketplace.''},
Proceedings of the Annual ACM Symposium on User Interface Software and Technology. ACM, 2015. (UIST'15 Poster)

{\bf Ryo Suzuki}, 
{\it ``Toward a Community Enhanced Programming Education.''}, 
Proceedings of the CHI Conference on Human Factors in Computing Systems. ACM, 2015. (CHI'15 Workshop)

{\bf Ryo Suzuki}, 
{\it ``Interactive and Collaborative Source Code Annotation.''}, 
Proceedings of the International Conference on Software Engineering. IEEE, 2015. (ICSE'15 Poster)

{\bf Ryo Suzuki}, 
{\it ``Network Thresholds and Multiple Equilibria in the Diffusion of Content-based Platforms.''},
Proceedings of the International Conference on Web and Internet Economics. Springer, 2014. (WINE'14 Poster)

% {\bf Ryo Suzuki}, {\it "Incentive Structure on Open Source Software Community: Case Study of GitHub."} Economics and Computer Science Workshop at the University of Tokyo, 2014

% {\bf Ryo Suzuki}, {\it "Diffusion Process and Take-off Conditions of the Online Platform."} Economics and Computer Science Workshop at the University of Tokyo, 2014
\end{rSection}


\begin{rSection}{Awards and Honors}

{\bf Nakajima Foundation Scholarship} \hfill {\em November 2014} \\
{\bf KAKENHI Grants-in-Aid for Scientific Research} \hfill {\em April 2013} \\
{\bf JSPS Research Fellow DC1} \hfill {\em April 2013} \\
{\bf JASSO Fellow (Total Exemption for Particularly Outstanding Students) } \hfill {\em March 2013} \\
{\bf Tohso Foundation Scholorship} \hfill {\em April 2010} \\

{\bf Business Model Competition Japan 2014 Microsoft Award} \hfill {\em February 2014} \\
{\bf Tech Crunch Disrupt Tokyo 2013 Finalist} \hfill {\em November 2013} \\
{\bf 1st Prize Winner of University of Tokyo Entrepreneur Dojo} \hfill {\em October 2012} \\
% {\bf Honer of MOVIDA School} \hfill {\em May 2012} \\
\end{rSection}


\begin{rSection}{Teaching Experience}

{\bf Teaching Assistant at University of Colorado Boulder} \hfill {\em January 2017 - May 2017} \\
Soft Robotics for Prof. Mark D. Gross

{\bf Teaching Assistant at University of Tokyo} \hfill {\em October 2012 - February 2013} \\
Microeconomic Policy (Graduate) for Prof. Dan Sasaki

{\bf Teaching Assistant at International Christian University} \hfill {\em October 2012 - February 2013} \\
Statistics (Undergraduate) for Prof. Takuya Kaneko

{\bf Teaching Assistant at University of Tokyo} \hfill {\em April 2012 - August 2012} \\
Mathematics II (Graduate) for Prof. Kazuya Kamiya

{\bf Teaching Assistant at Tokyo Institute of Technology} \hfill {\em October 2010 - February 2011} \\
Advanced Macroeconomics (Graduate) for Prof. Takumi Naito

\end{rSection}


\begin{rSection}{Work Experience}

{\bf CTO at Dada, Inc} \hfill {\em August 2012 - March 2014} \\
Development of Samenos (http://samenos.com), a platform for artists, creators, and designers.

{\bf Software Engineer at Howtelevision, Inc} \hfill {\em December 2011 - December 2012} \\
Development of iOS application for Gaishishukatsu.com (http://gaishishukatsu.com).

{\bf Data Analyst at Manavee} \hfill {\em January 2012 - March 2012} \\
Analysis of user data at Manvee (http://manavee.com), a MOOC for high school students in Japan.

\end{rSection}


\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{3ex}} l }
Programming Languages & Node.js/JavaScript, C/C++, Python, Ruby, Objective-C \\
Development Framework & OpenGL, WebGL, OpenCV, Tensorflow, React  \\
Tools & OnShape, Solidworks, Adobe Illustrator, Adobe After Effects \\
Electronics & Altium Designer, Eagle

% Databases & MySQL, PostgreSQL, MongoDB, Redis, Memcached \\
% Protocols \& APIs & JSON, REST, XML  \\
\end{tabular}

\end{rSection}



\end{document}
